A Decision Procedure for (Co)datatypes in SMT Solvers\thanks{In memoriam Morgan Deters 1979--2015}

### 2016-04-11 sister/sister.tex
updated ref
more

The original version of this paper was presented at the CADE-25 conference in
Berlin, Germany \cite{reynolds-blanchette-2015-codata}. An more comprehensive
article %, including detailed proofs,
will appear in a special issue of the
\emph{Journal of Automated Reasoning}. We refer to these for a description of
related work.
%\cite{reynolds-blanchette-201x-codata2}.

@@

%We now show (FIXME) the termination and correctness of the calculus.
%Correctness means the following:
%If there exists a closed derivation tree with root node
%$\Ec$, then $\Ec$ is %$\thD$-
%unsatisfiable; and if there exists
%a derivation tree with root node $\Ec$ that contains a saturated node, then
%$\Ec$ is %$\thD$-
%satisfiable.
We state the following properties of derivation trees generated by the calculus.

@@

\looseness=-1
By Theorems~1, 2, and 3, the
calculus is sound and complete for the universal theory of (co)datatypes. We may
rightly call it a decision procedure for that theory.
The proof of solution soundness is constructive in that it provides a
method for constructing a model for a saturated configuration.

@@

This work is part of a wider program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving.
We are currently interfacing CVC4's finite model finding capabilities
for generating counterexamples in proof assistants
\cite{reynolds-et-al-2015-smt}.
%as an alternative to Nitpick;
The acyclicity and uniqueness rules are
crucial to exclude spurious counterexamples.
%As future work, it would be useful to implement
%proof reconstruction for (co)data\-type inferences in Isabelle.
%In addition, it might be worthwhile to
%extend SMT solvers with dedicated support for (co)recursion.

>>>>

The original version of this paper was presented at the 25th
Conference on Automated Deduction (CADE-25) in
Berlin, Germany \cite{reynolds-blanchette-2015-codata}. An more comprehensive
article %, including detailed proofs,
will appear in a special issue of the
\emph{J.\ Autom.\ Reasoning}. % \cite{reynolds-blanchette-201x-codata3}.
We refer to these for a description of related work.
%\cite{reynolds-blanchette-201x-codata2}.

@@

%We now show (FIXME) the termination and correctness of the calculus.
%Correctness means the following:
%If there exists a closed derivation tree with root node
%$\Ec$, then $\Ec$ is %$\thD$-
%unsatisfiable; and if there exists
%a derivation tree with root node $\Ec$ that contains a saturated node, then
%$\Ec$ is %$\thD$-
%satisfiable.
We proved the following properties of derivation trees generated by the calculus
\cite{reynolds-blanchette-2015-codata}.

@@

\looseness=-1
By Theorems~1, 2, and 3, the
calculus is sound and complete for the universal theory of (co)datatypes. We may
rightly call it a decision procedure for that theory.
The proof of solution soundness %is constructive in that it
provides a method for constructing a model for a saturated configuration.

@@

This work is part of a wider program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving.
We are currently interfacing CVC4's finite model finding capabilities
for generating counterexamples in proof assistants
\cite{reynolds-et-al-2016-smt}.
%as an alternative to Nitpick;
The acyclicity and uniqueness rules are
crucial to exclude spurious counterexamples.
%As future work, it would be useful to implement
%proof reconstruction for (co)data\-type inferences in Isabelle.
%In addition, it might be worthwhile to
%extend SMT solvers with dedicated support for (co)recursion.
